Relationships in the extremes and their influence on competition and coexistence

### 2021-06-22 paper/Paper.tex
failed previously to removed some files, committing changes so I can then try again

Modern coexistence theory (REFS) and its recent computational extensions \citep{Ellner_2016,Ellner_2019} 
%***DAN: Search for REF and replace all with appropriate citations
quantify the contributions of 
different mechanisms to species coexistence. But we show in Sup Mat section X
%***DAN: Make this reference to the sup mat an autolink, and write the section
that, for purely temporal variation, only one mechanism relates to tail associations: storage effects. 
We here define storage effects abstractly and then for the lottery model, using an approach and notation
similar to that of \cite{Ellner_2016} and \cite{Ellner_2019}.

>>>>

Modern coexistence theory \citep{Chesson_2000} and its recent computational extensions \citep{Ellner_2016,Ellner_2019} 
%***DAN: Search for REF and replace all with appropriate citations
quantify the contributions of 
different mechanisms to species coexistence. But we show in Sup Mat section X
%***DAN: Make this reference to the sup mat an autolink, and write the section
that, for purely temporal variation, only one mechanism relates to tail associations: storage effects. 
We here define storage effects abstractly and then for the lottery model, using an approach and notation
that follows elements of the presentations in \cite{Ellner_2016} and \cite{Ellner_2019} closely (and see
those papers for additional details and explanation). We 
return briefly to other mechanisms of coexistence in the Discussion.
%***DAN: Don't forget to do this. Basically want to say intuitively why tail associations don't influence those,
%though might be worth mentioning that events are getting more extreme. We have studied how *relationships*
%in the extremes influence coexistence, but probably worth studying (or cite papers if it's been done) how changes
%in the commonness and extremeness of extreme events themselves influence coexistence, and for that you'd have
%to also look at the other mechanisms. 
It is assumed that the growth rate $r_i(t)$ of species $i$ can be written as an increasing function of
an environment-dependent factor $E_i(t)$ and as a decreasing function of a competitive pressure, $C_i(t)$.
For the lottery model, we take $E_i(t)=B_i(t)$, henceforth assuming that fecundity depends strictly on
the environment. Competition $C_i(t)$ is taken to be
